Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-15 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
working on section of grouping buildings

Original buildings grow according to time $t$.
We put the original buildings in the same group if 
they grow to become too close.
We group buildings based on buffering.
The basic idea is that 
we buffer the original buildings with distance $\dtrm{G}$
and an additional distance $\dtrm{C}$
(We will talk about how to define $\dtrm{C}$ later).
If two buffers overlap, 
then the original buildings are put in the same group.

\begin{figure}[tb]
	\centering
	\includegraphics[]{CloseDetect}
	\caption{bla.}
	\label{fig:CloseDetect}
\end{figure}

>>>>

Original buildings grow according to time $t$.
We put the original buildings in the same group if 
they grow to become too close.
We group buildings based on buffering.
The basic idea is that 
we buffer the original buildings with distance $\dtrm{G}$
and an additional distance $d_{\epsilon, t}/2$
(the distance between two buildings should be at least $d_{\epsilon, t}$).
If two buffers overlap, 
then the original buildings are put in the same group.
However, as some parts of a building grow faster than other parts, 
this basic idea may cause problems.
An example is shown in \fig\ref{fig:CloseDetect}c and~d.
In \fig\ref{fig:CloseDetect}d, 
the buffers of building $p$ and the buffer of building $q$ overlap each other, 
but the two buffers do not overlap with the buffer of building $r$.

\begin{figure}[tb]
	\centering
	\includegraphics[]{CloseDetect}
	\caption{Group buildings based on buffering.
		(a) original buildings.
		(b) bridges detected to aggregate the three buildings.
		(c) grow the original buildings with distance $\dtrm{G}$.
		(d) buffer the grown buildings in (c) 
		with distance $d_{\epsilon, t} /2$ using round joins.
		(e) buffer the original buildings 
		with distance $\alpha \dtrm{G}+d_{\epsilon, t}/2 $ 
		using round joins, where $\alpha=2$.
		(f) according to the buffer in (e), 
		we put the three original buildings in the same group.
		We aggregate the original buildings by adding the two bridges 
		and grow the aggregated building with distance $\dtrm{G}$.
	}
	\label{fig:CloseDetect}
\end{figure}
